\begin{thebibliography}{99}
\addcontentsline{toc}{chapter}{Bibliography}

\bibitem{label} Autoren: Titel, Verlag, \url{http://...}, Datum.

\bibitem{lisg} Livio Sgier: Bazo - A Cryptocurrency from Scratch, 2017.

\bibitem{webnfc} Kenneth Rohde Christiansen, Zoltan Kis, Alexander Shalamov: Web NFC API, \url{https://w3c.github.io/web-nfc/}, accessed 2nd January 2018.


\bibitem{androidnfc} Android NFC, \url{https://developer.android.com/guide/topics/connectivity/nfc/nfc.html}, accessed 10th December 2017.

\bibitem{corenfc} Apple Inc: Core NFC, \url{https://developer.apple.com/documentation/corenfc}, 2017.

\bibitem{gobind} Golang: gobind Documentation, \url{https://godoc.org/golang.org/x/mobile/cmd/gobind}, 2017.

\bibitem{bip21} Nils Schneider, Matt Corallo: URI Scheme\url{https://github.com/bitcoin/bips/blob/master/bip-0021.mediawiki}, 2012.

\bibitem{proofofstake} Simon Bachmann:  \url{https://..}, 2017.

\bibitem{ripplelib} Ripple-lib  \url{https://github.com/ripple/ripple-lib/blob/develop/docs/samples/payment.js}, 20XX.

\bibitem{safari11release} Apple Inc: Safari 11.0  \url{https://developer.apple.com/library/content/releasenotes/General/WhatsNewInSafari/Safari_11_0/Safari_11_0.html}, 2017.

\bibitem{ios11release} Apple Inc: iOS 11 available tomorrow \url{https://www.apple.com/chde/newsroom/2017/09/ios-11-available-tomorrow/}, 2017.

\bibitem{undefined} Undefined: null \url{https://somehost.com}, 2000.

\bibitem{serviceworkers} Alex Russell, Jungkee Song, Jake Archibald, Marijn Kruisselbrink : Service Workers \url{https://www.w3.org/TR/service-workers-1/}, 2017.

\bibitem{manifest} Marcos Caceres, 
Kenneth Rohde Christiansen, Mounir Lamouri, Anssi Kostiainen, Rob Dolin: Web App Manifest\url{https://w3c.github.io/manifest/}, 2017.

\bibitem{applemetatags} Apple Inc: Supported Meta Tags \url{https://developer.apple.com/library/content/documentation/AppleApplications/Reference/SafariHTMLRef/Articles/MetaTags.html}, 2017.

\bibitem{localstoragetest} World Wide Web Consortium (W3C): Implementation Report\url{https://w3c.github.io/test-results/webstorage/all
}.
\bibitem{localstorage} Ian Hickson: Web Storage\url{https://www.w3.org/TR/webstorage/}, 2016.
\bibitem{webcrypto} Mark Watson: Web Crypto API\url{https://www.w3.org/TR/WebCryptoAPI/}, 2017.

\bibitem{vuex} Vue.js: Vuex\url{https://vuex.vuejs.org/}, 2017.

\bibitem{myethwallet} MyEtherWallet.com\url{https://www.myetherwallet.com/}, accessed 29th December 2017.

\bibitem{p2ppayments} Terri Bradford, William R. Keeton: New Person-to-Person
Payment Methods: Have Checks Met Their Match?\url{https://www.myetherwallet.com/},p54, Federal Reserve Bank of Kansas City Economic Review 2012.

\bibitem{p2ppadoption} Leif Erik Kleivene: P2P Mobile Payments: Investigating the factors of adoption among students in Germany\url{http://lipisadvisors.com/wp-content/uploads/2017/01/White-Paper-P2P-mobile-payments.pdf}, 2016.

\bibitem{p2ptypes} Fiserv, Inc: The Four Pillars of Mobile Payments - Immediate Opportunities\url{https://www.fiserv.com/resources/Four_Pillars_Mobile_Payment_1404.pdf}, 2014.

\bibitem{bitcoinmobile} 
Mobile Payments and Bitcoin: Concluding Reflections on the Digital Upheaval in Payments \url{https://link.springer.com/content/pdf/10.1057\%2F978-1-137-57512-8.pdf} in Gabriella Gimigliano: Bitcoin and Mobile Payments, p281, 2014.

\bibitem{bitcoinclients}
Rostislav Skudnov: Bitcoin clients\url{http://publications.theseus.fi:80/bitstream/handle/10024/47166/Skudnov_Rostislav.pdf}, 2012.

\bibitem{pwas}
Google: Progressive Web Apps\url{https://developers.google.com/web/progressive-web-apps/}, accessed 30th December 2017.

\bibitem{securitychrome}
Google: Prefer Secure Origins For Powerful New Features \url{http://www.chromium.org/Home/chromium-security/prefer-secure-origins-for-powerful-new-features}, accessed 30th December 2017.

\bibitem{masteringbitcoin}
Mastering Bitcoin: Unlocking Digital Crypto-Currencies, O'Reilly Media, 2014.

\bibitem{webnfcpeer}
WebNFC Community Group: Issues, \url{https://github.com/w3c/web-nfc/issues/139}, accessed 31th December 2017.
\bibitem{origintrials}The Chromium Projects: Origin Trials, \url{https://www.chromium.org/blink/origin-trials}, accessed 2nd January 2018.
\bibitem{nfcforum}NFC Forum: About the technology, \url{https://nfc-forum.org/
}, accessed 2nd January 2018.

\bibitem{blep2p}Bluetooth SIG Inc: Low energy: Point-to-Point, \url{Bluetooth LE: Point-to-Point
}, accessed 2nd January 2018.

\bibitem{blegatt}Bluetooth SIG Inc: GATT Overview, \url{https://www.bluetooth.com/specifications/gatt/generic-attributes-overview}, accessed 2nd January 2018.

\bibitem{webble}François Beaufort, Google Inc: Interact with Bluetooth devices on the Web, \url{https://developers.google.com/web/updates/2015/07/interact-with-ble-devices-on-the-web}, accessed 2nd January 2018.

\bibitem{instascan}Coinblesk: coinblesk-frontend-instascan
, \url{https://github.com/coinblesk/coinblesk-frontend-instascan
}, accessed 3rd January 2018.

\bibitem{shapeapispec}Miguel Casas-Sanchez (Google Inc.): Accelerated Shape Detection in Images, \url{https://wicg.github.io/shape-detection-api/}, accessed 3rd January 2018.

\bibitem{shapeapinotes}W3C: Shape Detection API Specification 
- Current Related Efforts and Workarounds, \url{https://github.com/WICG/shape-detection-api#current-related-efforts-and-workarounds-wrench}, accessed 3rd January 2018.

\bibitem{webshareapi} Paul Kinlan, Sam Thorogood (Google Inc): Introducing the Web Share API
, \url{https://developers.google.com/web/updates/2016/09/navigator-share}, accessed 3rd January 2018.
\bibitem{websharespec} Matt Giuca (Google Inc): Web Share API
, \url{https://wicg.github.io/web-share/
}, accessed 3rd January 2018.

\bibitem{standalonetoolchain} Google Inc: Standalone Toolchains, \url{https://developer.android.com/ndk/guides/standalone_toolchain.html}, accessed 3rd January 2018.
\bibitem{gobuild} Golang: Generate go files by processing source, \url{https://golang.org/cmd/go/#hdr-Generate_Go_files_by_processing_source}, accessed 3rd January 2018.

\bibitem{coinbleskfrontend} Coinblesk: coinblesk-frontend \url{https://github.com/coinblesk/coinblesk-frontend
}, accessed 3rd January 2018.

\bibitem{bazoblockexplorer} Luc Boillat: Bazo Block Explorer \url{https://github.com/lucBoillat/BazoBlockExplorer
}, accessed 3rd January 2018.

\bibitem{webrtcimplreport} World Wide Web Consortium: Real-time Communication Between Browsers: Implementation Report \url{https://wpt.fyi/webrtc}, accessed 3rd January 2018.

\bibitem{lighthouse} Google Inc: Lighthouse \url{https://developers.google.com/web/tools/lighthouse/
}, accessed 8th January 2018.

\bibitem{pwachecklist} Google Inc: Progressive Web Application Checklist \url{https://developers.google.com/web/progressive-web-apps/checklist}, accessed 8th January 2018.


\end{thebibliography}


